\textsf{Are large language models superhuman chemists?}

### 2024-03-24 src/tex/ms.tex
discussion reviewed

Our findings also highlight the nuanced tradeoff between breadth and depth of evaluation frameworks. 
The analysis of model performance on different topics shows that the performance of models varies widely across topics. 
But even within a topic, the performance of models can vary widely depending on the type of question and the reasoning required to answer it.

The current evaluation frameworks for \glspl{llm} are mostly designed to measure the performance of the models on specific tasks. 
They cannot easily be used to evaluate systems, or models built for scientific applications. Thus, we had on little understanding of the capabilities of \glspl{llm} in the chemical sciences.
Our work,  shows that carefully curated benchmarks can provide a more nuanced understanding of the capabilities of \glspl{llm} in the chemical sciences.
It lays the groundwork for the development of more advanced systems that can be used in the chemical sciences and highlights the importance of continued development of evaluation frameworks for systematic improvement of safe and useful \glspl{llm}.
Our findings also illustrate that more focus is needed in the development of better human-model interaction frameworks given that models are not able to estimate their own limitations.

While our findings indicate many areas for further improvement of \gls{llm}-based systems, it is also important to realize that clearly defined metrics have been the key for the progress of many fields of \gls{ml} such computer vision. 
We thus believe that although current systems are far from reasoning like a chemist our open source \chembench framework will be a stepping stone for the development of systems that might come closer to this goal.

>>>>

Our findings also highlight the nuanced tradeoff between breadth and depth of evaluation frameworks. 
The analysis of model performance on different topics shows that the performance of models varies widely across topics. 
But even within a topic, the performance of models can vary significantly depending on the type of question and the reasoning required to answer it.

The current evaluation frameworks for \glspl{llm} are mostly designed to measure the performance of the models on specific tasks. 
They cannot easily be used to evaluate systems, or models built for scientific applications. As a result, we only had limited understanding of the capabilities of \glspl{llm} in the chemical sciences.
Our work shows that carefully curated benchmarks can provide a deeper understanding of the capabilities of \glspl{llm} in the chemical sciences.
It lays the groundwork for the development of more advanced systems that can be used in the chemical sciences and highlights the importance of continued development of evaluation frameworks for systematic improvement of safe and useful \glspl{llm}.
Our findings also illustrate that more focus is needed in the development of better human-model interaction frameworks given that models are not able to estimate their own limitations.

While our findings indicate many areas for further improvement of \gls{llm}-based systems, it is also important to realize that clearly defined metrics have been the key for the progress of many fields of \gls{ml}, such as computer vision. 
We believe that while current systems are far from reasoning like a chemist, our open-source \chembench framework will be a stepping stone for the development of systems that might come closer to this goal.
